NeuronUnit: Collaboratively Testing the Validity of Neuroscientific Models

### 2013-11-30 NeurounitFrontiers/Paper.tex
Updated ipython notebook figure

\subsection{Test Suites and Score Matrices} A collection of tests intended to be run on the same model can be put together to form a test suite.
The following is a test suite that could be used for a simplified version of the QSNMC, as described above:  
\begin{python}
CA1_suite = sciunit.TestSuite([CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_ism_test])
\end{python}
Like a single test, a test suite is capable of judging one or more models. The result is a score matrix much like the one diagramed in Fig. \ref{fig:sciunit_overview}.
\begin{python}
scores = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
\end{python}
A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.  For example, the score matrix might be visualized as an HTML table inside an IPython notebook recording the execution of the test suite.

\begin{figure}%[18]{r}{1\textwidth}
\includegraphics[scale=0.65]{table.png}
\caption{A record matrix for SciUnit tests}
\label{fig:scidash_matrix}
\vspace{-5px}
\end{figure}
\vspace{-10px}
\leavevmode

>>>>

\subsection{Test Suites and Score Matrices} A collection of tests intended to be run on the same model can be put together to form a test suite.
The following is a test suite that could be used for a simplified version of the QSNMC, as described above:  
\begin{python}
CA1_suite = sciunit.TestSuite([CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_ism_test])
\end{python}
Like a single test, a test suite is capable of judging one or more models. The result is a score matrix much like the one diagramed in Fig. \ref{fig:sciunit_overview}.
\begin{python}
scores = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
\end{python}
A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.  For example, the score matrix might be visualized as a hyperlinked table inside an IPython notebook containing the specification and execution of the test suite (Fig. \ref{fig:scidash_matrix}). Such notebooks are stored in test repositories like \textit{hippocampus\_tests}.

\begin{figure}%[18]{r}{1\textwidth}
\centering
\includegraphics[scale=0.55]{table-ipy.pdf}
\caption{A score matrix for a SciUnit test suite, visualized as a hyperlinked table inside an IPython notebook stored in a test repository like \textit{hippocampus\_tests}.}
\label{fig:scidash_matrix}
\vspace{-5px}
\end{figure}
\vspace{-10px}
\leavevmode
